\documentclass[a4paper, 12pt]{article}
\usepackage[usenames,dvipsnames,table]{xcolor}
\usepackage{fullpage}
\usepackage[top=0.5in, bottom=1in, left=1.0in, right=1.0in]{geometry}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{pgfornament}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{xspace}
\usepackage{lastpage}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{colortbl}



%opening
\renewcommand*{\familydefault}{\sfdefault}


\newcommand{\epv}[1]{\ensuremath{\left< #1 \right>}\xspace}
\newcommand{\variance}{\ensuremath{\text{Var}}}
\newcommand{\unit}[1]{\;\textrm{#1}}
\newcommand{\kwd}[1]{\textbf{\textcolor{Brown}{#1}}}
%\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\definecolor{cobalt}{rgb}{0.0, 0.28, 0.67}
\titleformat{\section}
{\normalfont\sffamily\large\bfseries\color{cobalt}}
{\thesection}{0em}{}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
%\cfoot{\pgfornament[height=1em, ydelta=-0.4em]{11} \thepage \;\pgfornament[height=1em, ydelta=-0.4em]{14}}

\pagenumbering{gobble}
\begin{document}

\begin{center}
	\textcolor{orange}{\Huge{\textsc{Pattern Recognition}}}\\
	\pgfornament[width=0.7\textwidth, color=white!30!black]{89}
\end{center}

%\begin{enumerate}[label={\textbf{Problem {\theenumi}}}]
%	\setlength\itemsep{1em}
%\end{enumerate}
%\setitemize{wide}
\begin{itemize}[leftmargin=1in]
\item [\textcolor{cobalt}{\textbf{Instructor:}}] Piti Ongmongkolkul(piti.ong@mahidol.ac.th)

\end{itemize}

\section*{Grading Scheme}

Subject to change.

\begin{center}
\setlength{\arrayrulewidth}{2pt} 
\rowcolors{1}{blue!10!white}{white}
\begin{tabular}{lr}

\arrayrulecolor{cobalt}\hline
Weekly Assignment \hspace{2cm} & 30 \% \\

Fun Project & 10 \% \\

Midterm \hspace{2cm} & 30 \% \\

Final \hspace{2cm} & 30 \% \\
\hline
\end{tabular}
\end{center}

\section*{Goal}

 The class covers many machine learning algorithm with emphasis on supervised learning. As the main goal of this class is to develop you intuition on how to build a classification system. Knowing the exact formula/algorithm is much less important than gaining the intuition. Keep this in mind when you do exercise in class. Think along, make a lot of alternative guess(why not this? what's wrong with that?), comes up with a lot of ideas(how about this?), and ask tons of questions.


\section*{Suggested Resources}

Books: Pattern Recognition and Machine Learning By Bishop, Learning from Data by Yaser S. Abu-Mostafa

Online Resources:
Scikit Learn Documentation is a good start. Andrew Ng Coursera is also a very good one. Or Search youtube for Caltech ML course.

\section*{Canvas}

This course will utilize canvas. Make sure you sign up and enroll before the end of the first week at \url{https://canvas.instructure.com/enroll/37G9JT}.

\section*{Tentative Schedule}

\begin{center}
\rowcolors{1}{blue!10!white}{white}
\setlength{\arrayrulewidth}{2pt} 
\begin{tabular}{cl}
	\arrayrulecolor{cobalt}\hline
    \textbf{Week 1 }& Basic Tools \& Naive Bayes \\
    \textbf{Week 2 }& Gradient Descent \& Linear Regression\\
    \textbf{Week 3 }& Logistic Regression \& Nearest Neighborhood \\
    \textbf{Week 4 }& Generalization \& Regularization \\
    \textbf{Week 5 }& Model Selections \& Cross Validation\\
    \textbf{Week 6 }& Midterm\\
    \textbf{Week 7 }& Multiclass Problem\\
    \textbf{Week 8}& Clustering Problem\\
    \textbf{Week 9 }& SVM\\
    \textbf{Week 10 }& SVM\\
    \textbf{Week 11}& Collaborative Filtering\\
    \textbf{Week 12}& Collaborative Filtering\\
	\hline
\end{tabular}
\end{center}
\end{document}